Associations of environmental and human factors with altered rodent populations in West Africa: A scoping review

### 2021-03-24 reports/manuscript.Rmd
updated manuscript

>>>>

From the included studies in 13 West African countries 131 distinct species were trapped. The majority were from the order Rodentia (102) with Muridae (83) being the largest family of rodents, followed by Gliridae (6), Nesomyidae (4), Sciuridae (3), Ctenodactylidae (2) and Anomaluridae, Dipodidae, Hystricidae and Thryonomidae (all 1). The next most represented orders were the Soricomorpha (25), Erinaceomorpha (3) and a single Afrosoricida.
